---
title: "gemR data documentation"
output: 
  html_document: 
    df_print: paged
    theme: simplex
    toc: yes
    toc_float: yes
---

<style>
    body {font-family: 'Helvetica Neue', Helvetica, Arial, sans-serif;}
    .table {width: 20%}
    .list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {background-color: #00346b; border-color: #00346b; opacity: 0.8;}
    h1, h2, h3 {color: #00346b;}
</style>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, comment = FALSE, warning = FALSE)

options(readr.num_columns = 0)

library(tidyverse)

getCSVPaths <- function(type){
  
  folderPath <- paste0("../Data/GEMdataInput/", type)
  csvPaths <- list.files(folderPath, full.names = TRUE)
  
  return(csvPaths)
  
}

getCSVInfo <- function(csv_name, type){
  
  df <- read_csv(csv_name) %>% 
    mutate_all(as.character)
  
  df_cols <- colnames(df)
  
  print( 
    df_cols[!(df_cols %>% str_detect("i_"))] %>% 
      knitr::kable(col.names = "Sets")
  )
  
  if(type == "Parameters"){
    
    print( 
      df_cols[df_cols %>% str_detect("i_")] %>% 
        knitr::kable(col.names = "Parameters")
    )
    
  }
  
  # cat("<p style='font-weight:bold'>First 5 rows</p>")
  # 
  # print(
  #   df %>%
  #     head(5) #%>%
  #     # knitr::kable()
  # )
  
}

```

## Purpose

To document where **sets**, **subsets**, **parameters** and **setup variables** can be found within the input CSVs.

## Sets

> *./Data/GEMdataInput/Sets*

```{r sets, out.width='100%', results="asis"}

setsCSVs <- getCSVPaths("Sets")

for(csv in setsCSVs){
  
  cat(
    "### "
    , csv %>% 
      str_extract("[:alnum:]+.csv") %>% 
      str_replace(".csv", ""), 
    " \n"
    , sep = ""
  ) 
  
  # cat("</br>", "\n")
  
  getCSVInfo(csv, type = "Sets")
  
  # cat("</br>", "\n \n")
  
  cat("***", "\n \n")
  
  # cat("</br>", "\n \n")
  
}

```

## Subsets

> *./Data/GEMdataInput/Subsets*

```{r subsets, out.width='100%', results="asis"}

subsetsCSVs <- getCSVPaths("Subsets")

for(csv in subsetsCSVs){
  
  cat(
    "### "
    , csv %>% 
      str_extract("[:alnum:]+.csv") %>% 
      str_replace(".csv", ""), 
    " \n"
    , sep = ""
  ) 
  
  # cat("</br>", "\n")
  
  getCSVInfo(csv, type = "Sets")
  
  # cat("</br>", "\n \n")
  
  cat("***", "\n \n")
  
  # cat("</br>", "\n \n")
  
}

```

## Parameters

> *./Data/GEMdataInput/Parameters*

```{r params, out.width='100%', results="asis"}

paramsCSVs <- getCSVPaths("Parameters")

for(csv in paramsCSVs){
  
  cat(
    "### "
    , csv %>% 
      str_extract("[:alnum:]+.csv") %>% 
      str_replace(".csv", "")
    , " \n"
    , sep = ""
  ) 
  
  # cat("</br>", "\n")
  
  getCSVInfo(csv, type = "Parameters")
  
  # cat("</br>", "\n \n")
  
  cat("***", "\n \n")
  
  # cat("</br>", "\n \n")
  
}

```

## Setup variables

### Globals

> *./Data/Setup/globalVariables.csv*

```{r globals}

read_csv("../Data/Setup/globalVariables.csv")

```

</br>

<hr>


### Scalars

> *./Data/Setup/scalarVariables.csv*

```{r scalars}

read_csv("../Data/Setup/scalarVariables.csv")

```


